Tail Flexibility in the Degrees of Preferential Attachment Networks

### 2025-03-27 paper.qmd
Updating figures

The IGPD has been shown to be in the same domain of attraction and has the same tail-index $\xi$ as the regular GPD with the same parameters by using the following quantity introduced by [@shimura12]:

$$
\Omega(F,n) = \left(\log\displaystyle\frac{\bar F (n+1)}{\bar F (n+2)}\right)^{-1} - \left(\log\displaystyle\frac{\bar F (n)}{\bar F (n+1)}\right)^{-1},
$$
the limit of this quantity if it exists and is non-zero is exactly the tail-index of the distribution $F$, and if the limit is zero then the distribution is in the Gumbel maximum domain of attraction. These results will be useful later on when trying to establish the tail behaviour of a network's limiting degree distribution.

@@

```{r, echo=FALSE, warning=FALSE, cache=TRUE, out.width="80%"}
#| fig-width: 8
#| fig-height: 8
#| fig-cap: Posterior estimates of paramters for data simulated from the proposed model with various combinations of ($\alpha$,$\beta$,$\varepsilon$) and $k_0=20$.
#| label: fig-rec2

library(gridExtra)
plt = readRDS('mcmc_plot.rds')
plot(plt)

@@

>>>>

@shimura12 introduces a quantity that will help in determining what domain of attraction a discrete distribution belongs to, that is:

@@

:::{#fig-rec2 out.width="80%"}
![: Posterior estimates of paramters for data simulated from the proposed model with various combinations of ($\alpha$,$\beta$,$\varepsilon$) and $k_0=20$.](mcmc_plot.jpg)
:::

@@

To demonstrate that the model is capturing the tail behaviour of the degree distributions @fig-gp_comp shows the tail heaviness based on samples from the MCMC for each network as well as the tail heaviness as estimated by fitting the GPD to the degrees for various thresholds.

```{r, echo=FALSE, warning=FALSE, cache=TRUE, out.width="80%"}
#| fig-width: 9
#| fig-height: 6
#| fig-cap: Posterior samples of shape parameter from model (blue) and GPD shape parameter (red) at various thresholds
#| label: fig-gp_comp

plt2 = readRDS('gp_plt.rds')

plot(plt2)

### 2025-03-27 paper.tex
Updating figures

The IGPD has been shown to be in the same domain of attraction and has
the same tail-index \(\xi\) as the regular GPD with the same parameters
by using the following quantity introduced by \citep{shimura12}:

\[
\Omega(F,n) = \left(\log\displaystyle\frac{\bar F (n+1)}{\bar F (n+2)}\right)^{-1} - \left(\log\displaystyle\frac{\bar F (n)}{\bar F (n+1)}\right)^{-1},
\] the limit of this quantity if it exists and is non-zero is exactly
the tail-index of the distribution \(F\), and if the limit is zero then
the distribution is in the Gumbel maximum domain of attraction. These
results will be useful later on when trying to establish the tail
behaviour of a network's limiting degree distribution.

@@

\includegraphics[width=0.8\textwidth,height=\textheight]{paper_files/figure-pdf/fig-rec2-1.pdf}

@@

\caption{\label{fig-rec2}Posterior estimates of paramters for data
simulated from the proposed model with various combinations of
(\(\alpha\),\(\beta\),\(\varepsilon\)) and \(k_0=20\).}

@@

>>>>

\citet{shimura12} introduces a quantity that will help in determining
what domain of attraction a discrete distribution belongs to, that is:

@@

\captionsetup{labelsep=none}

\begin{figure}[H]

{\centering \includegraphics{mcmc_plot.jpg}

@@

\caption{: Posterior estimates of paramters for data simulated from the
proposed model with various combinations of
(\(\alpha\),\(\beta\),\(\varepsilon\)) and \(k_0=20\).}

\caption{\label{fig-rec2}}

@@

To demonstrate that the model is capturing the tail behaviour of the
degree distributions Figure~\ref{fig-gp_comp} shows the tail heaviness
based on samples from the MCMC for each network as well as the tail
heaviness as estimated by fitting the GPD to the degrees for various
thresholds.

\includegraphics[width=0.8\textwidth,height=\textheight]{paper_files/figure-pdf/fig-gp_comp-1.pdf}

\caption{\label{fig-gp_comp}Posterior samples of shape parameter from
model (blue) and GPD shape parameter (red) at various thresholds}
